\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{titling}

\geometry{a4paper, margin=1in}

\title{Design Specifications}
\author{
    Brian Becerra\\
    \and
    Jason Salazar\\
    \and
    Krystal Lo\\
    \and
    Mark Canseco\\
    }
\date{April 2025}

\setlength{\droptitle}{6cm}

\pagestyle{fancy}
\fancyhead[L]{Snapshot Objectives}
\fancyhead[R]{Page \thepage}
\fancyfoot[C]{}

\begin{document}

\begin{titlepage}
\maketitle
\thispagestyle{empty}
\end{titlepage}

\section*{Packages}
\begin{itemize}
    \item 
\end{itemize}

\section*{Dependencies}
\begin{itemize}
    \item \textbf{Front-End (Angular 4):}
    \begin{itemize}
        \item \textbf{Node.js (version 6.9 or higher):} JavaScript runtime environment.
        \item \textbf{npm (version 3 or higher)} 
        \item \textbf{Angular CLI (@angular/cli)}
        \item \textbf{Angular Framework (@angular/*):} Includes the core Angular modules and libraries:
        \begin{itemize}
            \item \texttt{@angular/core}
            \item \texttt{@angular/common}
            \item \texttt{@angular/compiler}
            \item \texttt{@angular/platform-browser}
            \item \texttt{@angular/platform-browser-dynamic}
            \item \texttt{@angular/router}
            \item \texttt{@angular/forms}
            \item \texttt{@angular/http}
        \end{itemize}
        These are managed by npm.
        \item \textbf{TypeScript}
    \end{itemize}
    \item \textbf{Back-End (Java/Spring):}
    \begin{itemize}
        \item \textbf{Java 8 (JDK or OpenJDK):} The programming language and development kit.
        \item \textbf{Spring Framework (Spring Boot):} The core Java enterprise framework. Key dependencies include:
        \begin{itemize}
            \item \texttt{spring-boot-starter-web}
        \end{itemize}
        Dependencies are managed by \textbf{Gradle}.
        \item \textbf{Gradle:} Build automation tool for Java projects.
        \item \textbf{Microsoft SQL Server JDBC Driver (sqljdbc42.jar):} A Java Database Connectivity driver for connecting to Microsoft SQL Server.
    \end{itemize}
    \item \textbf{Database Management:}
    \begin{itemize}
        \item \textbf{Microsoft SQL Server:} The relational database management system.
        \item \textbf{Microsoft SQL Server Management Studio (SSMS)}
        \item \textbf{DBeaver (Alternative):} Universal database tool.
    \end{itemize}
\end{itemize}

\section*{Libraries}
\begin{itemize}
    \item \textbf{RxJS} 
\end{itemize}

\end{document}
